---
title: "Calculating SNP heritabilities Protocol"
output: html_notebook
---

# WEIGHTINGS using LDAK5

Calculate Weighted relationship Matrices for the regions of interest using LDAK5

```{bash}

## Prepare data to compute weightings
# listALL is a list of all the markers and GGC1 is the prefix of the genotypic data in plink format
ldak5 --cut-weights sectionsGP --bfile GGC1 --extract listALL

## Calculate weightings for each section
# the number of sections is stored in sectionsGP/section.number 
for j in {1..896}; do ldak5 --calc-weights sectionsGP/ --bfile GGC1 --extract ALLsnps --section $j; done

## Join weightings across sections
ldak5 --join-weights sectionsGP –extract-index ALLsnps

```

# Calculating GRM for variance component analysis

Here we are gonna calculate the GRM for the intergenic dReg regions that intersect with the Category #2


Get the markers for the section we have

### dREG intersection with II

```{bash}

#We are working with fewer markers here so lets extend the regions a little bit
more dREG_conserved_relax.bed | awk '{print $1"\t"$2-500"\t"$3+500"\t"$4"\t"$5}' > dREG_500.bed

#Intersect the position of the regions with the positions of all available SNPS
bedtools intersect -a dREG_500.bed -b /home/NVME/Pro-seq/Quantitative/BEDs/I2_LDAK.bed  -wa -wb > dReg500.intersect

#Get uniq markers intersecting with my segments
awk '{print$9}' dReg500.intersect | sort -n | uniq > dReg500.snps 

#Formatting the bed file for LDAK purposes
more dREG_500.bed | awk '{print"S"$1"_"$2, $1, $2, $3}' | sed 's/ /\t/g' > dREG_500.ldak

```

### Calculate GRMS 

```{bash}

#To calculate enrichment of DHS, first compute kinships from DHS SNPs, then its complement (i.e., subtract from genome-wide kinships), then perform two-way REML
ldak5 --cut-genes DREG --bfile GGC1 --genefile /home/NVME/Pro-seq/Quantitative/dREG/dREG_500.ldak--ignore-weights YES
ldak5 --calc-kins-direct DREG --bfile data --extract DREG/genes.predictors.used --weights sectionsGP/weights.all --power -0.25 --kinship-raw YES


echo -e "/home/NVME/Pro-seq/Quantitative/Predictions/GRMs/LDAK_old/kinshipall/kinships.all./DREG\n" > listsub
ldak5 --sub-grm not_DREG --mgrm listsub --kinship-raw YES


```

### GENOMIC PREDICTION CODE


Read the phenotypes

```{r}

phenos <- read.delim(file = "/home/NVME/Pro-seq/Quantitative/Predictions/phenos/Phenos.GGC1",sep = "\t", header = TRUE )
clones <- phenos$namescross

#Xclones <- gsub("2013_", "X2013_", clones, perl=TRUE)

phenos$CLONE <- clones


phenos$CLONE[37015:37026]
save(phenos, file = "/home/NVME/Pro-seq/Quantitative/Predictions/GRMs/LDAK/phenos.Rdata")

```

Load the relationship matrices

```{r}

ids <- read.delim(file = "/home/NVME/Pro-seq/Quantitative/Predictions/GRMs/LDAK_old/kinships/IDs", header = F, stringsAsFactors = F)
ids <- ids[,1]

DREG.grm <- read.delim(file = "/home/NVME/Pro-seq/Quantitative/Predictions/GRMs/LDAK/DREG.grm.raw", header = F, sep = " ")
DREG.grm <- DREG.grm[,-3012]
rownames(DREG.grm) <- ids  
colnames(DREG.grm) <- ids
DREG.grm <- as.matrix(DREG.grm)

EE.grm <- read.delim(file = "/home/NVME/Pro-seq/Quantitative/Predictions/GRMs/LDAK/not_DREG.grm.raw", header = F, sep = " ")
EE.grm <- EE.grm[,-3012]
rownames(EE.grm) <- ids  
colnames(EE.grm) <- ids
EE.grm <- as.matrix(EE.grm)

ids <- read.delim(file = "/home/NVME/Pro-seq/Quantitative/Predictions/LDAK/kinships/kinships.all.grm.id", sep = " ", header = F, stringsAsFactors = F)
ids <- ids[,1]

I2_LDAK.grm <- read.delim(file = "/home/NVME/Pro-seq/Quantitative/Predictions/LDAK/kinships/kinships.all.grm.raw", header = F, sep = " ")
I2_LDAK.grm <- I2_LDAK.grm[,-3012]
rownames(I2_LDAK.grm) <- ids  
colnames(I2_LDAK.grm) <- ids
I2_LDAK.grm <- as.matrix(I2_LDAK.grm)


save(DREG.grm, file = "/home/NVME/Pro-seq/Quantitative/Predictions/GRMs/LDAK/DREG/DREG.grm")
save(EE.grm, file = "/home/NVME/Pro-seq/Quantitative/Predictions/GRMs/LDAK/DREG/EE.grm")
save(I2_LDAK.grm, file = "/home/NVME/Pro-seq/Quantitative/Predictions/LDAK/kinships/I2_LDAK.grm")

DREG.grm[1:5,1:5]
I2_LDAK.grm[1:5,1:5]

```

Run this in the CBSU

```{r}

library(foreach)
library(doParallel)

load("/home/NVME/Pro-seq/Quantitative/Predictions/GRMs/LDAK/DREG/DREG.grm")
load("/home/NVME/Pro-seq/Quantitative/Predictions/GRMs/LDAK/DREG/EE.grm")
load("/home/NVME/Pro-seq/Quantitative/Predictions/GRMs/LDAK/phenos.Rdata")

traits <- c("logRTWT", "DM")

K <- DREG.grm
individuals<-rownames(K)
sampleinds<-sample(individuals,400)

K<-K[rownames(K)%in%sampleinds,colnames(K)%in%sampleinds]

Klist<- list(DREG.grm[rownames(DREG.grm)%in%sampleinds,colnames(DREG.grm)%in%sampleinds], EE.grm[rownames(EE.grm)%in%sampleinds,colnames(EE.grm)%in%sampleinds])

pizza=2
ProseqDREG <- foreach(a=traits, pizza=icount(), .inorder=TRUE) %dopar% { 
  require(EMMREML); trait=traits[pizza]
  data1 <- phenos[!is.na(phenos[,trait]),]
  if(trait %in% c("logRTWT","logRTNO","logFYLD","logSHTWT")){ data1 <- data1[!is.na(data1$NOHAV),] }
  data1<-data1[data1$CLONE%in%sampleinds,]
  data1$CLONE          <- factor(as.character(data1$CLONE),levels=rownames(K))
  data1$LOC.YEAR       <- factor(as.character(data1$LOC.YEAR))
  data1$LOC.YEAR.RANGE <- factor(paste(data1$LOC.YEAR,data1$TRIAL.NAME,data1$RANGE,sep="."))
  
  Zg = model.matrix(~data1$CLONE-1)
  Zr = model.matrix(~data1$LOC.YEAR.RANGE-1)
  
  Zlist<-list(Zg,Zr,Zg)
  Klist<-list(Klist[[1]],diag(ncol(Zr)),Klist[[2]])
  
  if(trait %in% c("logRTWT","logRTNO","logFYLD","logSHTWT")){ X = model.matrix(~1+LOC.YEAR + NOHAV,data=data1) } else { X = model.matrix(~1+LOC.YEAR,data=data1) }
  y = data1[,trait]
  funout <- emmremlMultiKernel(y=y, X=X, Z=Zlist, K=Klist, varuhat=F,PEVuhat=F) }
proctime <- proc.time() - proctime; proctime; save(ProseqDREG,proctime,file="/home/rjl278/PRO-seq/ProseqDREG.Rdata")


```
```{r}

library(foreach)
library(doParallel)

load("/workdir/rjl278/DREG/DREG.grm")
load("/workdir/rjl278/DREG/EE.grm")
load("/workdir/rjl278/DREG/phenos.Rdata")

traits <- c("logRTWT", "logRTNO", "logFYLD", "logSHTWT","DM")
Klist<- list(DREG.grm, EE.grm)
K <- DREG.grm

ProseqDREG <- foreach(a=traits, pizza=icount(), .inorder=TRUE) %dopar% { 
  require(EMMREML); trait=traits[pizza]
  data1 <- phenos[!is.na(phenos[,trait]),]
  if(trait %in% c("logRTWT","logRTNO","logFYLD","logSHTWT")){ data1 <- data1[!is.na(data1$NOHAV),] }
  
  data1$CLONE          <- factor(as.character(data1$CLONE),levels=rownames(K))
  data1$LOC.YEAR       <- factor(as.character(data1$LOC.YEAR))
  data1$LOC.YEAR.RANGE <- factor(paste(data1$LOC.YEAR,data1$TRIAL.NAME,data1$RANGE,sep="."))
  
  Zg = model.matrix(~data1$CLONE-1)
  Zr = model.matrix(~data1$LOC.YEAR.RANGE-1)
  
  Zlist<-list(Zg,Zr,Zg)
  Klist<-list(Klist[[1]],diag(ncol(Zr)),Klist[[2]])
  
  if(trait %in% c("logRTWT","logRTNO","logFYLD","logSHTWT")){ X = model.matrix(~1+LOC.YEAR + NOHAV,data=data1) } else { X = model.matrix(~1+LOC.YEAR,data=data1) }
  y = data1[,trait]
  funout <- emmremlMultiKernel(y=y, X=X, Z=Zlist, K=Klist, varuhat=F,PEVuhat=F) }
proctime <- proc.time() - proctime; proctime; save(ProseqDREG,proctime,file="/home/rjl278/PRO-seq/ProseqDREG.Rdata")


```


```{r}

library(foreach)
library(doParallel)

load("I2_LDAK.grm")
load("phenos.Rdata")

traits <- c("logFYLD", "DM")
K      <- I2_LDAK.grm

onekernel <- foreach(a=traits, pizza=icount(), .inorder=TRUE) %dopar% { 
  require(EMMREML); trait=traits[pizza]
  data1 <- phenos[!is.na(phenos[,trait]),]
  
  if(trait %in% c("logRTWT","logRTNO","logFYLD","logSHTWT")){ data1 <- data1[!is.na(data1$NOHAV),] }
  
  data1$CLONE          <- factor(as.character(data1$CLONE),levels=rownames(K))
  data1$LOC.YEAR       <- factor(as.character(data1$LOC.YEAR))
  data1$LOC.YEAR.RANGE <- factor(paste(data1$LOC.YEAR,data1$TRIAL.NAME,data1$RANGE,sep="."))
  
  Zg = model.matrix(~data1$CLONE-1)
  Zr = model.matrix(~data1$LOC.YEAR.RANGE-1)
  
  if(trait %in% c("logRTWT","logRTNO","logFYLD","logSHTWT")){ X = model.matrix(~1+LOC.YEAR + NOHAV,data=data1) } else { X = model.matrix(~1+LOC.YEAR,data=data1) }
  
  y = data1[,trait]
  funout <- emmremlMultiKernel(y=y, X=X, Z=list(Zg,Zr), K=list(K,diag(ncol(Zr))), varuhat=T,PEVuhat=T) }
proctime<-proc.time() - proctime; proctime; save(onekernel,proctime,file="onekernel.Rdata")



```




12
```{r}

library(foreach)
library(doParallel)

load("I2_LDAK.grm")
load("phenos.Rdata")

traits <- c("logFYLD", "DM")
K      <- I2_LDAK.grm

onekernel <- foreach(a=traits, pizza=icount(), .inorder=TRUE) %dopar% { 
  require(EMMREML); trait=traits[pizza]
  data1 <- phenos[!is.na(phenos[,trait]),]
  
  if(trait %in% c("logRTWT","logRTNO","logFYLD","logSHTWT")){ data1 <- data1[!is.na(data1$NOHAV),] }
  
  data1$CLONE          <- factor(as.character(data1$CLONE),levels=rownames(K))
  data1$LOC.YEAR       <- factor(as.character(data1$LOC.YEAR))
  data1$LOC.YEAR.RANGE <- factor(paste(data1$LOC.YEAR,data1$TRIAL.NAME,data1$RANGE,sep="."))
  
  Zg = model.matrix(~data1$CLONE-1)
  Zr = model.matrix(~data1$LOC.YEAR.RANGE-1)
  
  if(trait %in% c("logRTWT","logRTNO","logFYLD","logSHTWT")){ X = model.matrix(~1+LOC.YEAR + NOHAV,data=data1) } else { X = model.matrix(~1+LOC.YEAR,data=data1) }
  
  y = data1[,trait]
  funout <- emmremlMultiKernel(y=y, X=X, Z=list(Zg,Zr), K=list(K,diag(ncol(Zr))), varbetahat=FALSE,varuhat=FALSE, PEVuhat=FALSE, test=FALSE) }
proctime<-proc.time() - proctime; proctime; save(onekernel,proctime,file="onekernel.Rdata")




```


12b
```{r}

phenos <- read.delim(file = "/home/NVME/Pro-seq/Quantitative/Predictions/phenos/Phenos.GGC1",sep = "\t", header = TRUE )
clones <- phenos$namescross

Xclones <- gsub("2013_", "X2013_", clones, perl=TRUE)

phenos$CLONE <- Xclones


phenos$CLONE[37015:37026]
save(phenos, file = "/home/NVME/Pro-seq/Quantitative/Predictions/GRMs/tmp/phenos.Rdata")


XIDs <- gsub("2013_", "X2013_", colnames(I2_LDAK.grm), perl = TRUE)
colnames(I2_LDAK.grm) <- XIDs
rownames(I2_LDAK.grm) <- XIDs

save(I2_LDAK.grm, file = "/home/NVME/Pro-seq/Quantitative/Predictions/GRMs/tmp/I2_LDAK.grm")

```

```{r}
library(foreach)
library(doParallel)

load("III.grm")
load("phenos.Rdata")

traits <- c("DM")
Klist  <- list(III.grm)
K      <- III.grm

desesperacion <- foreach(a=traits, pizza=icount(), .inorder=TRUE) %dopar% { 
 
  require(EMMREML); trait=traits[pizza]
  data1 <- phenos[!is.na(phenos[,trait]),]
  
  if(trait %in% c("logRTWT","logRTNO","logFYLD","logSHTWT")){ data1 <- data1[!is.na(data1$NOHAV),] }
  
  data1$CLONE          <- factor(as.character(data1$CLONE),levels=rownames(K))
  data1$LOC.YEAR       <- factor(as.character(data1$LOC.YEAR))
  data1$LOC.YEAR.RANGE <- factor(paste(data1$LOC.YEAR,data1$TRIAL.NAME,data1$RANGE,sep="."))
  
  Zg = model.matrix(~data1$CLONE-1)
  Zr = model.matrix(~data1$LOC.YEAR.RANGE-1)
  
  Zlist<-list(Zg,Zr)
  Klist<-list(Klist[[1]],diag(ncol(Zr)))
  
  if(trait %in% c("logRTWT","logRTNO","logFYLD","logSHTWT")){ X = model.matrix(~1+LOC.YEAR + NOHAV,data=data1) } else { X = model.matrix(~1+LOC.YEAR,data=data1) }
  
  y = data1[,trait]
  funout <- emmremlMultiKernel(y=y, X=X, Z=Zlist, K=Klist) }
proctime <- proc.time() - proctime; proctime; save(desesperacion,proctime,file="desesperacion.Rdata")



```

MANUAL

```{r}
library(foreach)
library(doParallel)

load("III.grm")
load("phenos.Rdata")

traits <- c("DM")
Klist  <- list(III.grm)
K      <- III.grm

desesperacion <- foreach(a=traits, pizza=icount(), .inorder=TRUE) %dopar% { 
 
  require(EMMREML); trait=traits[pizza]
  data1 <- phenos[!is.na(phenos[,trait]),]
  
  if(trait %in% c("logRTWT","logRTNO","logFYLD","logSHTWT")){ data1 <- data1[!is.na(data1$NOHAV),] }
  
  data1$CLONE          <- factor(as.character(data1$CLONE),levels=rownames(K))
  data1$LOC.YEAR       <- factor(as.character(data1$LOC.YEAR))
  data1$LOC.YEAR.RANGE <- factor(paste(data1$LOC.YEAR,data1$TRIAL.NAME,data1$RANGE,sep="."))
  
  Zg = model.matrix(~data1$CLONE-1)
  Zr = model.matrix(~data1$LOC.YEAR.RANGE-1)
  
  Zlist<-list(Zg,Zr)
  Klist<-list(Klist[[1]],diag(ncol(Zr)))
  
  if(trait %in% c("logRTWT","logRTNO","logFYLD","logSHTWT")){ X = model.matrix(~1+LOC.YEAR + NOHAV,data=data1) } else { X = model.matrix(~1+LOC.YEAR,data=data1) }
  
  y = data1[,trait]
  funout <- emmremlMultiKernel(y=y, X=X, Z=Zlist, K=Klist) }
proctime <- proc.time() - proctime; proctime; save(desesperacion,proctime,file="desesperacion.Rdata")



```

## DENIZ FTW

```{r}

library(foreach)
library(doParallel)

load("/home/NVME/Pro-seq/Quantitative/Predictions/GRMs/LDAK/DREG/DREG.grm")
load("/home/NVME/Pro-seq/Quantitative/Predictions/GRMs/LDAK/DREG/EE.grm")
load("/home/NVME/Pro-seq/Quantitative/Predictions/GRMs/LDAK/phenos.Rdata")

DREG.grm  <-  dR.grm

K <- DREG.grm
individuals<-rownames(K)
sampleinds<-sample(individuals,400)
sampleinds
K<-K[rownames(K)%in%sampleinds,colnames(K)%in%sampleinds]

Klist<- list(DREG.grm[rownames(DREG.grm)%in%sampleinds,colnames(DREG.grm)%in%sampleinds], EE.grm[rownames(EE.grm)%in%sampleinds,colnames(EE.grm)%in%sampleinds])

#pizza=2
#ProseqDREG <- foreach(a=traits, pizza=icount(), .inorder=TRUE) %dopar% { 
  
require(EMMREML) 
trait="DM"
data1 <- phenos[!is.na(phenos[,trait]),]
if(trait %in% c("logRTWT","logRTNO","logFYLD","logSHTWT")){ data1 <- data1[!is.na(data1$NOHAV),] }
data1<-data1[data1$CLONE%in%sampleinds,]
data1$CLONE          <- factor(as.character(data1$CLONE),levels=rownames(K))
data1$LOC.YEAR       <- factor(as.character(data1$LOC.YEAR))
data1$LOC.YEAR.RANGE <- factor(paste(data1$LOC.YEAR,data1$TRIAL.NAME,data1$RANGE,sep="."))
  
Zg = model.matrix(~data1$CLONE-1)
Zr = model.matrix(~data1$LOC.YEAR.RANGE-1)
  
Zlist<-list(Zg,Zr,Zg)
Klist<-list(Klist[[2]],diag(ncol(Zr)),Klist[[1]])
  
if(trait %in% c("logRTWT","logRTNO","logFYLD","logSHTWT")){ X = model.matrix(~1+LOC.YEAR + NOHAV,data=data1) } else { X = model.matrix(~1+LOC.YEAR,data=data1) }
y = data1[,trait]

funout <- emmremlMultiKernel(y=y, X=X, Z=Zlist, K=Klist) 


ids <- read.delim(file = "/home/NVME/Pro-seq/Quantitative/Predictions/LDAK/IDs", header = F, stringsAsFactors = F)
ids <- ids[,1]

dR.grm <- read.delim(file = "/home/NVME/Pro-seq/Quantitative/Predictions/LDAK/dREG.grm.raw", header = F, sep = " ")
dR.grm <- dR.grm[,-3012]
rownames(dR.grm) <- ids  
colnames(dR.grm) <- ids
dR.grm <- as.matrix(dR.grm)

EE.grm <- read.delim(file = "/home/NVME/Pro-seq/Quantitative/Predictions/LDAK/not_dREG.grm.raw", header = F, sep = " ")
EE.grm <- EE.grm[,-3012]
rownames(EE.grm) <- ids  
colnames(EE.grm) <- ids
EE.grm <- as.matrix(EE.grm)





gc()
```


```{r}



load("/home/NVME/Pro-seq/Quantitative/Predictions/GRMs/LDAK/phenos.Rdata")


IDs <- read.delim(file = "/home/NVME/Pro-seq/Quantitative/dREG/LD/dREG/IDs", header = F, stringsAsFactors = F)
ids <- IDs[,1]

DREG.grm <- read.delim(file = "/home/NVME/Pro-seq/Quantitative/dREG/LD/dREG/DREG.grm.raw", header = F, sep = " ")
DREG.grm <- DREG.grm[,-3012]
rownames(DREG.grm) <- ids  
colnames(DREG.grm) <- ids
DREG.grm <- as.matrix(DREG.grm)

EE.grm <- read.delim(file = "/home/NVME/Pro-seq/Quantitative/dREG/LD/dREG/not_DREG.grm.raw", header = F, sep = " ")
EE.grm <- EE.grm[,-3012]
rownames(EE.grm) <- ids  
colnames(EE.grm) <- ids
EE.grm <- as.matrix(EE.grm)

```


```{r}

K <- DREG.grm
individuals<-rownames(K)
Klist<- list(DREG.grm,EE.grm)

sampleinds<-sample(individuals,400)
sampleinds
K<-K[rownames(K)%in%sampleinds,colnames(K)%in%sampleinds]

Klist<- list(DREG.grm[rownames(DREG.grm)%in%sampleinds,colnames(DREG.grm)%in%sampleinds], EE.grm[rownames(EE.grm)%in%sampleinds,colnames(EE.grm)%in%sampleinds])

#pizza=2
#ProseqDREG <- foreach(a=traits, pizza=icount(), .inorder=TRUE) %dopar% { 
  
require(EMMREML) 
trait="logRTWT"
data1 <- phenos[!is.na(phenos[,trait]),]
if(trait %in% c("logRTWT","logRTNO","logFYLD","logSHTWT")){ data1 <- data1[!is.na(data1$NOHAV),] }
data1<-data1[data1$CLONE%in%sampleinds,]
data1$CLONE          <- factor(as.character(data1$CLONE),levels=rownames(K))
data1$LOC.YEAR       <- factor(as.character(data1$LOC.YEAR))
data1$LOC.YEAR.RANGE <- factor(paste(data1$LOC.YEAR,data1$TRIAL.NAME,data1$RANGE,sep="."))
  
Zg = model.matrix(~data1$CLONE-1)
Zr = model.matrix(~data1$LOC.YEAR.RANGE-1)
  
Zlist<-list(Zg,Zr,Zg)
Klist<-list(Klist[[2]],diag(ncol(Zr)),Klist[[1]])
  
if(trait %in% c("logRTWT","logRTNO","logFYLD","logSHTWT")){ X = model.matrix(~1+LOC.YEAR + NOHAV,data=data1) } else { X = model.matrix(~1+LOC.YEAR,data=data1) }
y = data1[,trait]

funout <- emmremlMultiKernel(y=y, X=X, Z=Zlist, K=Klist) 

```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
