---
title: "R Notebook"
output: html_notebook
---



```{r}

source("http://bioconductor.org/biocLite.R")
biocLite("metagene")

library(metagene)
```

Load BAM files paths

```{r}

bam_files <- c("/home/NVME/Pro-seq/Second/Mapping/white_forward.bam", "/home/NVME/Pro-seq/Second/Mapping/white_reverse.bam")

bam_files
names(bam_files) <- c("Forward", "Reverse") 

```


Load coordinates

```{r}

regions <- get_demo_regions()
regions <- c("/home/NVME/Pro-seq/Second/Metagene/Chr1_positive.bed", "/home/NVME/Pro-seq/Second/Metagene/Chr1_negative.bed")

regions

```

Make the design matrix

```{r}

design <- data.frame(Samples = c(bam_files[1], bam_files[2]),
                     align1 = c(1,2))

design$Samples <- paste0(system.file("extdata", package="metagene"), "/",
                         design$Samples)

design
```

PLOTTING THE things

```{r}

#Initialize
mg <- metagene$new(regions = regions, bam_files = bam_files)

# Plotting
mg$plot(title = "Demo metagene plot")


a<- mg$produce_matrices()
a$get_matrices()




df <- mg$get_data_frame()

df [1:5, 1:5]
```



PLOT

```{r}


library(ggthemes)
library(extrafont)
library(ggplot2)


metagene            <- read.delim(file = "/home/NVME/Pro-seq/Second/Metagene/metagene.txt")
colnames(metagene)  <- c("axis", "coverage", "Pro (+)", "Pro (-)")

dim(metagene)
metageneplot <- matrix(0, ncol = 3 , nrow = dim(metagene)[1]*2)
metageneplot <- as.data.frame(metageneplot)
colnames(metageneplot)    <- c("Distance from TSS (5'end)","Normalized reads", "Strand")

reads    <- c(metagene$`Pro (+)`, metagene$`Pro (-)`)
distance <- c(metagene$axis, metagene$axis) 
strand   <- c(rep(x = "Pro(+)", dim(metagene)[1]), rep(x = "Pro(-)", dim(metagene)[1]))

metageneplot[,1] <- as.integer(distance) * -1 
metageneplot[,2] <- as.numeric(reads)
metageneplot[,3] <- strand




p1 <- ggplot() + geom_line(aes(y = `Normalized reads`, x =  `Distance from TSS (5'end)`, colour = Strand), size=1.3,
                           data = metageneplot, stat="identity") +
  theme(legend.position="bottom", legend.direction="horizontal",
        legend.title = element_blank()) +
  #scale_x_continuous(breaks=seq(2006,2014,1)) +
  #labs(x="Year", y="USD million") +
  ggtitle("Metagene Plot Cassava Pro-seq read") +
  scale_color_manual(values=fill) +
  theme(axis.line.x = element_line(size=1, colour = "black"),
        axis.line.y = element_line(size=1, colour = "black"),
        panel.grid.major = element_line(colour = "#d3d3d3"), panel.grid.minor = element_blank(),
        panel.border = element_blank(), panel.background = element_blank()) +
  theme(plot.title = element_text(size = 14, family = "Tahoma", face = "bold"),
        text=element_text(family="Tahoma"),
        axis.text.x=element_text(colour="black", size = 10),
        axis.text.y=element_text(colour="black", size = 10),
        legend.key=element_rect(fill="white", colour="white"))

p1

```





```{r}


metagene            <- read.delim(file = "/home/NVME/Pro-seq/Second/Metagene/metagene_long__TTS.txt")
colnames(metagene)  <- c("axis", "coverage", "Pro (+)", "Pro (-)")

dim(metagene)
metageneplot <- matrix(0, ncol = 3 , nrow = dim(metagene)[1]*2)
metageneplot <- as.data.frame(metageneplot)
colnames(metageneplot)    <- c("Distance from TSS (5'end)","Normalized reads", "Strand")

reads    <- c(metagene$`Pro (+)`, metagene$`Pro (-)`)
distance <- c(metagene$axis, metagene$axis) 
strand   <- c(rep(x = "Pro(+)", dim(metagene)[1]), rep(x = "Pro(-)", dim(metagene)[1]))

metageneplot[,1] <- as.integer(distance) * -1 
metageneplot[,2] <- as.numeric(reads)
metageneplot[,3] <- strand

delete        <- which(metageneplot[,1] < -1500)
metageneplot  <- metageneplot[-delete,]


p5 <- ggplot() + geom_line(aes(y = `Normalized reads`, x =  `Distance from TSS (5'end)`, colour = Strand), size=1.3,
                           data = metageneplot, stat="identity") +
  theme(legend.position="bottom", legend.direction="horizontal",
        legend.title = element_blank()) +
  #scale_x_continuous(breaks=seq(2006,2014,1)) +
  labs(x="Distance from TTS (5'end)") +
  ggtitle("Metagene Plot Cassava Pro-seq read") +
  scale_color_manual(values=fill) +
  theme(axis.line.x = element_line(size=1, colour = "black"),
        axis.line.y = element_line(size=1, colour = "black"),
        panel.grid.major = element_line(colour = "#d3d3d3"), panel.grid.minor = element_blank(),
        panel.border = element_blank(), panel.background = element_blank()) +
  theme(plot.title = element_text(size = 14, family = "Tahoma", face = "bold"),
        text=element_text(family="Tahoma"),
        axis.text.x=element_text(colour="black", size = 10),
        axis.text.y=element_text(colour="black", size = 10),
        legend.key=element_rect(fill="white", colour="white"))

p5

```

```{r}

p3 <- ggplot() + geom_line(aes(y = `Normalized reads`, x =  `Distance from TSS (5'end)`, colour = Strand), size=1.3,
                           data = metageneplot, stat="identity") +
  theme(legend.position="bottom", legend.direction="horizontal",
        legend.title = element_blank()) +
  #scale_x_continuous(breaks=seq(2006,2014,1)) +
  labs(x="Distance from TTS (3'end)") +
  ylim(0, 0.155) +
  ggtitle("Metagene Plot Cassava Pro-seq read") +
  scale_color_manual(values=fill) +
  theme(axis.line.x = element_line(size=1, colour = "black"),
        axis.line.y = element_line(size=1, colour = "black"),
        panel.grid.major = element_line(colour = "#d3d3d3"), panel.grid.minor = element_blank(),
        panel.border = element_blank(), panel.background = element_blank()) +
  theme(plot.title = element_text(size = 14, family = "Tahoma", face = "bold"),
        text=element_text(family="Tahoma"),
        axis.text.x=element_text(colour="black", size = 10),
        axis.text.y=element_text(colour="black", size = 10),
        legend.key=element_rect(fill="white", colour="white"))

p3


```

# PLOTS READY

## WHITE

### TSS

```{r}


library(ggthemes)
library(extrafont)
library(ggplot2)
library(wesanderson)
library(tidyr)
library(magrittr)
library(dplyr)

metagene            <- read.delim(file = "/home/NVME/Pro-seq/Second/Metagene/white/metagene_white_TSS.txt")
colnames(metagene)  <- c("axis", "coverage", "Pro (+)", "Pro (-)")

dim(metagene)
metageneplot <- matrix(0, ncol = 3 , nrow = dim(metagene)[1]*2)
metageneplot <- as.data.frame(metageneplot)
colnames(metageneplot)    <- c("Distance from TSS (5'end)","Normalized reads", "Strand")

reads    <- c(metagene$`Pro (+)`, metagene$`Pro (-)`)
distance <- c(metagene$axis, metagene$axis) 
strand   <- c(rep(x = "Pro(+)", dim(metagene)[1]), rep(x = "Pro(-)", dim(metagene)[1]))

metageneplot[,1] <- as.integer(distance) * -1 
metageneplot[,2] <- as.numeric(reads)
metageneplot[,3] <- strand

color <- wes_palette("Cavalcanti1")
fill <- c(color[1], color[2])

p1 <- ggplot() + geom_line(aes(y = `Normalized reads`, x =  `Distance from TSS (5'end)`, colour = Strand), size=1.3,
                           data = metageneplot, stat="identity") +
  theme(legend.position="bottom", legend.direction="horizontal",
        legend.title = element_blank()) +
  #scale_x_continuous(breaks=seq(2006,2014,1)) +
  #labs(x="Year", y="USD million") +
  ylim(0, 0.20)+
  ggtitle("Metagene Plot Cassava Pro-seq read") +
  scale_color_manual(values=fill) +
  theme(axis.line.x = element_line(size=1, colour = "black"),
        axis.line.y = element_line(size=1, colour = "black"),
        panel.grid.major = element_line(colour = "#d3d3d3"), panel.grid.minor = element_blank(),
        panel.border = element_blank(), panel.background = element_blank()) +
  theme(plot.title = element_text(size = 14, family = "Tahoma", face = "bold"),
        text=element_text(family="Tahoma"),
        axis.text.x=element_text(colour="black", size = 10),
        axis.text.y=element_text(colour="black", size = 10),
        legend.key=element_rect(fill="white", colour="white"))

p1

```

### TTS

```{r}

metagene            <- read.delim(file = "/home/NVME/Pro-seq/Second/Metagene/white/metagene_white_TTS.txt")
colnames(metagene)  <- c("axis", "coverage", "Pro (+)", "Pro (-)")

dim(metagene)
metageneplot <- matrix(0, ncol = 3 , nrow = dim(metagene)[1]*2)
metageneplot <- as.data.frame(metageneplot)
colnames(metageneplot)    <- c("Distance from TSS (5'end)","Normalized reads", "Strand")

reads    <- c(metagene$`Pro (+)`, metagene$`Pro (-)`)
distance <- c(metagene$axis, metagene$axis) 
strand   <- c(rep(x = "Pro(+)", dim(metagene)[1]), rep(x = "Pro(-)", dim(metagene)[1]))

metageneplot[,1] <- as.integer(distance) * -1 
metageneplot[,2] <- as.numeric(reads)
metageneplot[,3] <- strand

metageneplot <- metageneplot %>%
  filter(`Distance from TSS (5'end)` > -1500)

color <- wes_palette("Cavalcanti1")
fill <- c(color[1], color[2])

p1 <- ggplot() + geom_line(aes(y = `Normalized reads`, x =  `Distance from TSS (5'end)`, colour = Strand), size=1.3,
                           data = metageneplot, stat="identity") +
  theme(legend.position="bottom", legend.direction="horizontal",
        legend.title = element_blank()) +
  #scale_x_continuous(breaks=seq(2006,2014,1)) +
  #labs(x="Year", y="USD million") +
  labs(x="Distance from TTS (3'end)") +
  ylim(0, 0.20)+
  ggtitle("Metagene Plot Cassava Pro-seq read") +
  scale_color_manual(values=fill) +
  theme(axis.line.x = element_line(size=1, colour = "black"),
        axis.line.y = element_line(size=1, colour = "black"),
        panel.grid.major = element_line(colour = "#d3d3d3"), panel.grid.minor = element_blank(),
        panel.border = element_blank(), panel.background = element_blank()) +
  theme(plot.title = element_text(size = 14, family = "Tahoma", face = "bold"),
        text=element_text(family="Tahoma"),
        axis.text.x=element_text(colour="black", size = 10),
        axis.text.y=element_text(colour="black", size = 10),
        legend.key=element_rect(fill="white", colour="white"))

p1

```

## OLD

###TSS

```{r}

metagene            <- read.delim(file = "/home/NVME/Pro-seq/Second/Metagene/old/metagene_old_TSS.txt")
colnames(metagene)  <- c("axis", "coverage", "Pro (+)", "Pro (-)")

dim(metagene)
metageneplot <- matrix(0, ncol = 3 , nrow = dim(metagene)[1]*2)
metageneplot <- as.data.frame(metageneplot)
colnames(metageneplot)    <- c("Distance from TSS (5'end)","Normalized reads", "Strand")

reads    <- c(metagene$`Pro (+)`, metagene$`Pro (-)`)
distance <- c(metagene$axis, metagene$axis) 
strand   <- c(rep(x = "Pro(+)", dim(metagene)[1]), rep(x = "Pro(-)", dim(metagene)[1]))

metageneplot[,1] <- as.integer(distance) * -1 
metageneplot[,2] <- as.numeric(reads)
metageneplot[,3] <- strand

#metageneplot <- metageneplot %>%
#  filter(`Distance from TSS (5'end)` > -1500)

color <- wes_palette("Cavalcanti1")
fill <- c(color[1], color[2])

p1 <- ggplot() + geom_line(aes(y = `Normalized reads`, x =  `Distance from TSS (5'end)`, colour = Strand), size=1.3,
                           data = metageneplot, stat="identity") +
  theme(legend.position="bottom", legend.direction="horizontal",
        legend.title = element_blank()) +
  #scale_x_continuous(breaks=seq(2006,2014,1)) +
  #labs(x="Year", y="USD million") +
  
  ylim(0, 0.20)+
  ggtitle("Metagene Plot Cassava Pro-seq read") +
  scale_color_manual(values=fill) +
  theme(axis.line.x = element_line(size=1, colour = "black"),
        axis.line.y = element_line(size=1, colour = "black"),
        panel.grid.major = element_line(colour = "#d3d3d3"), panel.grid.minor = element_blank(),
        panel.border = element_blank(), panel.background = element_blank()) +
  theme(plot.title = element_text(size = 14, family = "Tahoma", face = "bold"),
        text=element_text(family="Tahoma"),
        axis.text.x=element_text(colour="black", size = 10),
        axis.text.y=element_text(colour="black", size = 10),
        legend.key=element_rect(fill="white", colour="white"))

p1

```


###TTS

```{r}

metagene            <- read.delim(file = "/home/NVME/Pro-seq/Second/Metagene/old/metagene_old_TTS.txt")
colnames(metagene)  <- c("axis", "coverage", "Pro (+)", "Pro (-)")

dim(metagene)
metageneplot <- matrix(0, ncol = 3 , nrow = dim(metagene)[1]*2)
metageneplot <- as.data.frame(metageneplot)
colnames(metageneplot)    <- c("Distance from TSS (5'end)","Normalized reads", "Strand")

reads    <- c(metagene$`Pro (+)`, metagene$`Pro (-)`)
distance <- c(metagene$axis, metagene$axis) 
strand   <- c(rep(x = "Pro(+)", dim(metagene)[1]), rep(x = "Pro(-)", dim(metagene)[1]))

metageneplot[,1] <- as.integer(distance) * -1 
metageneplot[,2] <- as.numeric(reads)
metageneplot[,3] <- strand

metageneplot <- metageneplot %>%
  filter(`Distance from TSS (5'end)` > -1500)

color <- wes_palette("Cavalcanti1")
fill <- c(color[1], color[2])

p1 <- ggplot() + geom_line(aes(y = `Normalized reads`, x =  `Distance from TSS (5'end)`, colour = Strand), size=1.3,
                           data = metageneplot, stat="identity") +
  theme(legend.position="bottom", legend.direction="horizontal",
        legend.title = element_blank()) +
  #scale_x_continuous(breaks=seq(2006,2014,1)) +
  #labs(x="Year", y="USD million") +
  labs(x="Distance from TTS (3'end)") +
  ylim(0, 0.20)+
  ggtitle("Metagene Plot Cassava Pro-seq read") +
  scale_color_manual(values=fill) +
  theme(axis.line.x = element_line(size=1, colour = "black"),
        axis.line.y = element_line(size=1, colour = "black"),
        panel.grid.major = element_line(colour = "#d3d3d3"), panel.grid.minor = element_blank(),
        panel.border = element_blank(), panel.background = element_blank()) +
  theme(plot.title = element_text(size = 14, family = "Tahoma", face = "bold"),
        text=element_text(family="Tahoma"),
        axis.text.x=element_text(colour="black", size = 10),
        axis.text.y=element_text(colour="black", size = 10),
        legend.key=element_rect(fill="white", colour="white"))

p1

```

##WHITE INTERGENIC


###Intergenic

```{r}

metagene            <- read.delim(file = "/home/NVME/Pro-seq/Second/Metagene/white/metagene_intergenic.txt")
colnames(metagene)  <- c("axis", "coverage", "Pro (+)", "Pro (-)")

dim(metagene)
metageneplot <- matrix(0, ncol = 3 , nrow = dim(metagene)[1]*2)
metageneplot <- as.data.frame(metageneplot)
colnames(metageneplot)    <- c("Distance from TSS (5'end)","Normalized reads", "Strand")

reads    <- c(metagene$`Pro (+)`, metagene$`Pro (-)`)
distance <- c(metagene$axis, metagene$axis) 
strand   <- c(rep(x = "Pro(+)", dim(metagene)[1]), rep(x = "Pro(-)", dim(metagene)[1]))

metageneplot[,1] <- as.integer(distance) * -1 
metageneplot[,2] <- as.numeric(reads)
metageneplot[,3] <- strand

#metageneplot <- metageneplot %>%
#  filter(`Distance from TSS (5'end)` > -1500)

color <- wes_palette("FantasticFox1")
fill <- c(color[3], color[4])

p1 <- ggplot() + geom_line(aes(y = `Normalized reads`, x =  `Distance from TSS (5'end)`, colour = Strand), size=1.3,
                           data = metageneplot, stat="identity") +
  theme(legend.position="bottom", legend.direction="horizontal",
        legend.title = element_blank()) +
  #scale_x_continuous(breaks=seq(2006,2014,1)) +
  #labs(x="Year", y="USD million") +
#  ylim(0, 0.20)+
  labs(x="Distance from Intergenic Peak") +
  ggtitle("Metagene Plot Cassava Pro-seq read") +
  scale_color_manual(values=fill) +
  theme(axis.line.x = element_line(size=1, colour = "black"),
        axis.line.y = element_line(size=1, colour = "black"),
        panel.grid.major = element_line(colour = "#d3d3d3"), panel.grid.minor = element_blank(),
        panel.border = element_blank(), panel.background = element_blank()) +
  theme(plot.title = element_text(size = 14, family = "Tahoma", face = "bold"),
        text=element_text(family="Tahoma"),
        axis.text.x=element_text(colour="black", size = 10),
        axis.text.y=element_text(colour="black", size = 10),
        legend.key=element_rect(fill="white", colour="white"))

p1

```


###Intergenic ALL

```{r}

metagene            <- read.delim(file = "/home/NVME/Pro-seq/Second/Metagene/white/metagene_intergenic_all.txt")
colnames(metagene)  <- c("axis", "coverage", "Pro (+)", "Pro (-)")

dim(metagene)
metageneplot <- matrix(0, ncol = 3 , nrow = dim(metagene)[1]*2)
metageneplot <- as.data.frame(metageneplot)
colnames(metageneplot)    <- c("Distance from TSS (5'end)","Normalized reads", "Strand")

reads    <- c(metagene$`Pro (+)`, metagene$`Pro (-)`)
distance <- c(metagene$axis, metagene$axis) 
strand   <- c(rep(x = "Pro(+)", dim(metagene)[1]), rep(x = "Pro(-)", dim(metagene)[1]))

metageneplot[,1] <- as.integer(distance) * -1 
metageneplot[,2] <- as.numeric(reads)
metageneplot[,3] <- strand

#metageneplot <- metageneplot %>%
#  filter(`Distance from TSS (5'end)` > -1500)

color <- wes_palette("FantasticFox1")
fill <- c(color[3], color[4])

p1 <- ggplot() + geom_line(aes(y = `Normalized reads`, x =  `Distance from TSS (5'end)`, colour = Strand), size=1.3,
                           data = metageneplot, stat="identity") +
  theme(legend.position="bottom", legend.direction="horizontal",
        legend.title = element_blank()) +
  #scale_x_continuous(breaks=seq(2006,2014,1)) +
  #labs(x="Year", y="USD million") +
#  ylim(0, 0.20)+
  labs(x="Distance from Intergenic Peak") +
  ggtitle("Metagene Plot Cassava Pro-seq read") +
  scale_color_manual(values=fill) +
  theme(axis.line.x = element_line(size=1, colour = "black"),
        axis.line.y = element_line(size=1, colour = "black"),
        panel.grid.major = element_line(colour = "#d3d3d3"), panel.grid.minor = element_blank(),
        panel.border = element_blank(), panel.background = element_blank()) +
  theme(plot.title = element_text(size = 14, family = "Tahoma", face = "bold"),
        text=element_text(family="Tahoma"),
        axis.text.x=element_text(colour="black", size = 10),
        axis.text.y=element_text(colour="black", size = 10),
        legend.key=element_rect(fill="white", colour="white"))

p1

```


## Chloroplast

```{r}

metagene            <- read.delim(file = "/home/NVME/Pro-seq/Second/Metagene/Chloroplast/chloroplast_white_TSS.txt")
colnames(metagene)  <- c("axis", "coverage", "Pro (+)", "Pro (-)")

dim(metagene)
metageneplot <- matrix(0, ncol = 3 , nrow = dim(metagene)[1]*2)
metageneplot <- as.data.frame(metageneplot)
colnames(metageneplot)    <- c("Distance from TSS (5'end)","Normalized reads", "Strand")

reads    <- c(metagene$`Pro (+)`, metagene$`Pro (-)`)
distance <- c(metagene$axis, metagene$axis) 
strand   <- c(rep(x = "Pro(+)", dim(metagene)[1]), rep(x = "Pro(-)", dim(metagene)[1]))

metageneplot[,1] <- as.integer(distance) * -1 
metageneplot[,2] <- as.numeric(reads)
metageneplot[,3] <- strand

#metageneplot <- metageneplot %>%
#  filter(`Distance from TSS (5'end)` > -1500)

color <- wes_palette("FantasticFox1")
fill <- c(color[3], color[4])

p1 <- ggplot() + geom_line(aes(y = `Normalized reads`, x =  `Distance from TSS (5'end)`, colour = Strand), size=1.3,
                           data = metageneplot, stat="identity") +
  theme(legend.position="bottom", legend.direction="horizontal",
        legend.title = element_blank()) +
  #scale_x_continuous(breaks=seq(2006,2014,1)) +
  #labs(x="Year", y="USD million") +
#  ylim(0, 0.20)+
  labs(x="Distance 5' extreme") +
  ggtitle("Metagene Plot Cassava Pro-seq read") +
  scale_color_manual(values=fill) +
  theme(axis.line.x = element_line(size=1, colour = "black"),
        axis.line.y = element_line(size=1, colour = "black"),
        panel.grid.major = element_line(colour = "#d3d3d3"), panel.grid.minor = element_blank(),
        panel.border = element_blank(), panel.background = element_blank()) +
  theme(plot.title = element_text(size = 14, family = "Tahoma", face = "bold"),
        text=element_text(family="Tahoma"),
        axis.text.x=element_text(colour="black", size = 10),
        axis.text.y=element_text(colour="black", size = 10),
        legend.key=element_rect(fill="white", colour="white"))

p1

```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
